WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-09-16 ms.tex
More changes to abstract

\begin{abstract}
Advanced LIGO and Virgo should begin detecting gravitational waves from binary neutron star and neutron star\nobreakdashes--black hole mergers within the next few years. These sources are also predicted to power a variety of electromagnetic transients. Because these signatures can be fast and faint, locating and observing them hinges on rapidly inferring the sky location from the gravitational wave observations. MCMC methods for gravitational\nobreakdashes-wave parameter estimation can take hours or more. We describe a new, non-MCMC, fully deterministic Bayesian parameter estimation algorithm that takes just seconds to produce probability sky maps that are nearly as accurate.
\end{abstract}

>>>>

\begin{abstract}
Within the next few years, Advanced LIGO and Virgo should detect gravitational waves from binary neutron star and neutron star\nobreakdashes--black hole mergers. These sources are also predicted to power a broad array of electromagnetic transients. Because the X\nobreakdashes-ray and optical signatures can be faint and fade rapidly, observing them hinges on rapidly inferring the sky location from the gravitational wave observations. MCMC methods for gravitational\nobreakdashes-wave parameter estimation can take hours or more. We introduce BAYESTAR, a rapid, Bayesian, non-MCMC sky localization algorithm that takes just seconds to produce probability sky maps that are comparable in accuracy to the full analysis. Prompt localizations from BAYESTAR will make it possible to search electromagnetic counterparts of compact binary mergers.
\end{abstract}
